\documentclass[defaultstyle,11pt]{thesis}

\usepackage{enumitem}
\usepackage{fixltx2e}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{color}
\usepackage[tbtags]{amsmath}
\usepackage{textcomp}
\usepackage{subcaption}
\usepackage{longtable}
\usepackage{float}
\usepackage[top=25truemm,bottom=30truemm,left=25truemm,right=25truemm]{geometry}

%%%%%%%%%%%%   All the preamble material:   %%%%%%%%%%%%

\title{The Structure of Complex Networks across Domains}

\author{Kansuke}{Ikehara}

\otherdegrees{B.Eng., Fukuoka Univesity, 2014}

\degree{Master of Science}		%  #1 {long descr.}
	{M.S., Computer Science}		%  #2 {short descr.}

\dept{Department of}			%  #1 {designation}
	{Computer Science}		%  #2 {name}

\advisor{Prof.}				%  #1 {title}
	{Aaron Clauset}			%  #2 {name}

\reader{Prof.~Elizabeth Bradley}		%  2nd person to sign thesis
\readerThree{Prof.~Jordan Boyd-Graber}		%  3rd person to sign thesis

\abstract{ \OnePageChapter
	The structure of complex networks has been of interest in many scientific and engineering disciplines over the decades. A number of studies in the field have been focused on finding the common properties among different kinds of networks such as heavy-tail degree distribution, small-worldness and modular structure and trying to establish a theory of structural universality in complex networks. However, there is no comprehensive study of network structure across a diverse set of domains in order to explain the structural diversity we observe in the real-world networks. In this paper, we study 986 real-world networks of diverse domains ranging from ecological food webs to online social networks along with 575 networks generated from four popular network models. Our study utilizes a number of  machine learning techniques such as random forest and confusion matrix in order to show the relationships among network domains in terms of network structure. Our results indicate that there are some partitions of network categories in which networks are hard to distinguish based purely on network structure. We have foaund that these partitions of network categories tend to have similar underlying functions, constraints and/or generative mechanisms of networks even though networks in the same partition have different origins, e.g., biological processes, results of engineering by human being, etc. This suggests that the origin of a network, whether it's biological, technological or social, may not necessarily be a decisive factor of the formation of similar network structure. Our findings shed light on the possible direction along which we could uncover the hidden principles for the structural diversity of complex networks.
}
\dedication[Dedication]{	% NEVER use \OnePageChapter here.
	To my family, in America and Japan.
	}

\acknowledgements{	\OnePageChapter	% *MUST* BE ONLY ONE PAGE!
	First, I would like to thank Prof. Clauset for his guidance and support during my thesis project. He is, without any doubt, one of the smartest people I have ever met and I am deeply grateful to him for having intellectually stimulating discussions together. 
	
	I would like to also thank members in the Clauset lab for the constructive advice regarding my thesis project and giving me different perspectives in research and life as well.
	
	With my all heart, I deeply thank the people in International Horizons for everything I have been given here in Boulder, Colorado. 
	
	Lastly, I would like to thank my family in Okinawa, Japan. In my life filled with a number of failure and success, you have been truly supporting and loving me in any circumstance. 
	}

% \IRBprotocol{E927F29.001X}	% optional!

\ToCisShort	% use this only for 1-page Table of Contents

\LoFisShort	% use this only for 1-page Table of Figures
% \emptyLoF	% use this if there is no List of Figures

\LoTisShort	% use this only for 1-page Table of Tables
% \emptyLoT	% use this if there is no List of Tables

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%       BEGIN DOCUMENT...         %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\input chapter1.tex
\input chapter2.tex
\input chapter3.tex
\input chapter4.tex
\input chapter5.tex
\input chapter6.tex
\input chapter7.tex
\input chapter8.tex

%%%%%%%%%   then the Bibliography, if any   %%%%%%%%%
\bibliographystyle{ieeetr}	% or "siam", or "alpha", etc.
\nocite{*}		% list all refs in database, cited or not
\bibliography{reference}		% Bib database in "refs.bib"

%%%%%%%%%   then the Appendices, if any   %%%%%%%%%
%\appendix
%\input appendixA.tex
%\input appendixB.tex


\end{document}

